Market Simulator

### 2020-08-20 analysis/05_market_simulator.Rmd
small change

    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
    # beta_persona$p1_value[beta_persona$levels %in% input == '1'] <- 1
    # beta_persona$p1_value[beta_persona$levels %in% input == '2'] <- 2
    # beta_persona$p1_value[beta_persona$levels %in% input == '3'] <- 3
    # beta_persona$p1_value[beta_persona$levels %in% input == '4'] <- 4
    # beta_persona$p1_value[beta_persona$levels %in% input == '5'] <- 5
    # beta_persona$p1_value[beta_persona$levels %in% input == '6'] <- 6
    # beta_persona$p1_value[beta_persona$levels %in% input == '7'] <- 7

>>>>

    beta_persona$p1_value[beta_persona$levels %in% input$p1_political_pref] <- 1
